The Unicode Cookbook \linebreak for Linguists

### 2018-06-11 book/localmetadata.tex
ready for review two
migrate to newer class
add some of the proofreaders

\title{The Unicode Cookbook \linebreak for Linguists}
\subtitle{Managing writing systems using orthography profiles}
\BackTitle{Change backtitle in  localmetadata.tex}
\BackBody{Change backbody in  localmetadata.tex}
\dedication{Change dedication in localmetadata.tex}
\typesetter{Change typesetter in localmetadata.tex}
\proofreader{Change proofreaders in localmetadata.tex}
\author{Steven Moran \& Michael Cysouw}
\renewcommand{\lsISBN}{978--3--000000--00--0}                     
\renewcommand{\lsSeries}{dummyseries} 
% use lowercase acronym, e.g. sidl, eotms, tgdi
\renewcommand{\lsSeriesNumber}{99} 
%will be assigned when the book enters the proofreading stage
\renewcommand{\lsURL}{http://langsci-press.org/catalog/book/0} 
% contact the coordinator for the right number

>>>>

\title{The Unicode Cookbook \linebreak for Linguists}
\subtitle{Managing writing systems using orthography profiles}
\BackTitle{Change backtitle in  localmetadata.tex}
\BackBody{Change backbody in  localmetadata.tex}
% \dedication{Change dedication in localmetadata.tex}
\typesetter{Change typesetter in localmetadata.tex}
\proofreader{Sandra Auderset, Aleksandrs Berdičevskis, Rosey Billington, Simon Cozens, Aniefon Daniel, Bev Erasmus, Amir Ghorbanpour, David Lukeš, Hugh Paterson III, Stephen Pepper, Katja Politt, Felix Rau, James Tauber, Luigi Talamo, Jeroen van de Weijer, Viola Wiegand, Alena Witzlack-Makarevich, and Esther Yap}
\author{Steven Moran \and Michael Cysouw}
\renewcommand{\lsISBNdigital}{978-3-96110-090-3 }                     
\renewcommand{\lsISBNhardcover}{978-3-96110-091-0}                     
\renewcommand{\lsSeries}{tmnlp}  
\renewcommand{\lsSeriesNumber}{10}  
\renewcommand{\lsID}{176}
